\documentclass[letterpaper]{resume}
\usepackage{comment}
\setcounter{errorcontextlines}{100}
%\usepackage{paralist}

% Multi-colored rules! (John Q is desperate)
\definecolor{ruleendcolor}{rgb}{0.2, 0.2, 0.6}

\begin{document}

\author{Arseniy Y Zaostrovnykh}
\email{necto@frtk.ru}
\phone{+7(909)970-67 36}
\maketitle

\section{Areas of interest}
Math, graphs, physical simulation, UI, game-dev, lisp, compilers, code optimization, language design, robotics, development for mobile devices, pattern recognition, computer vision.

\section{Education}

\subsection{Graduate}

\affiliation[Master of Informatics and Computer Science]{Moscow Institute of Physics and Technology - MIPT, Moscow}{2012-2014}
\begin{itemize}
	\item In progress...
\end{itemize}

\affiliation[Bachelor of Applied Physics and Mathematics]{Moscow Institute of Physics and Technology - MIPT, Moscow}{2008-2012}
\begin{itemize}

	\item The Department of Radio Engineering.\\ The main modules include General Physics,
Theoretical Physics, Theoretical Mechanics, Mathematical Analysis, Complex Analysis, Differential Equations, Computational Mathematics, Linear Algebra, Equations of Mathematical Physics, A History of Philosophy, General Informatics, Operational Systems, Object Oriented Programming, Theory of Probabilities etc.
%\item Specialized in \emph{microprocessor design} and \emph{paralleling compilers} for the last two years.
\item Internship at {\bf Intel}
\item Graduation with honors
\item \emph{GPA}: {\bf 5.00} out of {\bf 5} (top 3\%)
\end{itemize}

\subsection{Successfully taken Stanford on-line courses}
\begin{itemize}
	\item Machine learning(Andrew Ng)
	\item Algorithms Design and Analysis Part I(Tim Roughgarden)
	\item Compilers (Alex Aiken)
\end{itemize}
\affiliation{Successfully taken the Robotics summer school in Imperial College of London, sponsored by Skolkovo}{2012}

\affiliation[additional Chemistry, Biology, Physics and Math classes]{Institute of Theoretical and Experimental Physics, Moscow}{2003-2008}

\affiliation{School \#179 Moscow Institute of Open Education, Moscow}{2005-2008}
\begin{itemize}
	\item A class with physical and mathematical bias
	\item {\bf A} scores for Chemistry, Biology, Geography, Physics, Maths, Computer Science
\end{itemize}

\affiliation[additional Math classes]{Moscow Center of Continuous Mathematical Education - MCCME, Moscow}{2003-2003}
\affiliation{MIPT - correspondence school of physics and mathematics}{2005-2007}
\affiliation{The municipal state comprehensive school of Obukhovo \#24, Noginsk region Moscow area}{1998-2005}
\pagebreak
\section{Work and practices experience}

\affiliation{Intel Corporation, Moscow}{2010-now}
\begin{itemize}
	\item Development of an optimizing binary translator from existing binary codes to the new parallel architecture.
\end{itemize}
\affiliation{OJS Co. ``Institute of Electronic Control Computers''}{2012}
\begin{itemize}
  \item Development of a technology of creation components for a base model of prosthesis, which can be controlled by impulses of a brain.
\end{itemize}
\affiliation{MIPT-Intel Laboratory}{2009-now}
\begin{itemize}
	\item Development of an open source QT-based graph-visualizing software http://code.google.com/p/mipt-vis/
        \item Mentoring of an open source scheme compiler http://code.google.com/p/mipt-scheme-compiler/
\end{itemize}
\affiliation{A laboratory of NetCracker}{2010-2011}
\begin{itemize}
	\item Java EE course
	\item Oracle SQL course
	\item Development of a GWT-based open source music-listening web service https://github.com/necto/natty 
\end{itemize}

\section{Skills Profile}
\subsection{Computer skills}
\begin{itemize}
	\item Participated in developing using C/C++ (work 3 years, academic 6 years experience), STL, QT, Java SE/EE/ME(1 year academ. exp.), XML, \LaTeX, x86/AVR ASM, Git, SVN, Vim, GWT, Maven 2, Common Lisp, SLIME, OpenGL, AJAX, HTML, CSS, SQL (Postgre/Oracle), MongoDB.
	\item Have an experience in the IDE such as: NetBeans, Vim, Emacs, Eclipse, WinAVR, Microsoft Visual Studio, Borland C++ Builder, Proteus, Micro-Cap, Code::Blocks, DevCpp.
	\item Understand computer architecture, operating systems, algorithm effectiveness, computational geometry, object-oriented and functional style programming, debugging process and REPL conception
	\item Worked and familiar with operating systems, such as Linux(Arch, Ubuntu), Windows 95/98/XP/7/Mobile.
	\item Have experience in a parallel programming using OpenMP and MPI libraries, posix threads
	\item Experience in working in a project with a million lines of source code.
	\item Had a summer practice in the Parallels\textsuperscript{\textregistered} inc.
	\item Have experience in game, user interface, physical engine development.
\end{itemize}

\subsection{Communication skills}
\begin{itemize}
	\item Took part in local, state and regional olympiads and conferences of mathematics, physics and biology. Have got a first prize and several second prizes. Have been a captain of a team to solve complicated physical several days-problems in interstate competition.
	\item Assisted in organization of a sport day for my department.
	\item I'm a praepostor of my study group.
        \item Gave several lectures for iLab students.
\end{itemize}

\subsection{Languages}
\begin{itemize}
	\item Russian - native
	\item English - C1-advanced(TOEFL 96)
	\item French - A2-pre-intermediate
\end{itemize}

\subsection{Sports}
\begin{itemize}
	\item I can do 29 pull-ups, more than a hundred push-ups.
        \item Did SAMBO for several years. I do swimming, cycling, roller skating, parkour, free running, sport dancing.
	\item I have got some awards on department sport competitions.
\end{itemize}


\emph{\bf References are available upon request}

\end{document}
